Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.

### 2021-06-24 manuscript/article.Rmd
made two experiments

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
CBSBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))

ss_exp_result <- CBSBPB_data
result_index <- 1

p1  <- plot_ss_result1(CBSBPB_data,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

@@

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
p2  <- plot_ss_result1(tmp2$ss_res[[1]],
                tmp2$CB_var_gmax_s,
                tmp2$CB_var_h_s,
                tmp2$SB_var_gmax_s,
                tmp2$SB_var_h_s,
                tmp2$PB_var_gmax_s,
                tmp2$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}

#ss_result1 <- ss_novar$ss_res[[1]]
#ss_result2 <- ss_var$ss_res[[1]]

p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
                             tmp2$ss_res[[1]],
                             xlims = c(-7, -1))

@@

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
CB_data <- readRDS(here("simulations/sim data/ss_res_grad_CB_var.RDS"))
tmp3 <- CB_data[20,]

p2  <- plot_ss_result1(tmp3$ss_res[[1]],
                tmp3$CB_var_gmax_s,
                tmp3$CB_var_h_s,
                tmp3$SB_var_gmax_s,
                tmp3$SB_var_h_s,
                tmp3$PB_var_gmax_s,
                tmp3$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}

#ss_result1 <- ss_novar$ss_res[[1]]
#ss_result2 <- ss_var$ss_res[[1]]

p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
                             tmp3$ss_res[[1]],
                             xlims = c(-7, -1))

@@

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
SB_data <- readRDS(here("simulations/sim data/ss_res_grad_SB_var.RDS"))
tmp4 <- SB_data[20,]

p2  <- plot_ss_result1(tmp4$ss_res[[1]],
                tmp4$CB_var_gmax_s,
                tmp4$CB_var_h_s,
                tmp4$SB_var_gmax_s,
                tmp4$SB_var_h_s,
                tmp4$PB_var_gmax_s,
                tmp4$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}

#ss_result1 <- ss_novar$ss_res[[1]]
#ss_result2 <- ss_var$ss_res[[1]]

p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
                             tmp4$ss_res[[1]],
                             xlims = c(-7, -1))

@@

@@

```{r ss_var3, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))

CBSBPB_data <- CBSBPB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results <- unnest(CBSBPB_data, cols = c(stability_measures))

results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = CB_var_gmax_s, y = hyst_range)) +
  geom_point()

>>>>

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("No diversity"), echo=FALSE}
CBSBPB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_CBSBPB_var.RDS"))
result_index1 <- 1
p1  <- plot_ss_result1(CBSBPB_data,
                result_index = result_index1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

@@

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in all functional groups"), echo=FALSE}
result_index2 <- 20
p2  <- plot_ss_result1(CBSBPB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and all functional groups."), echo=FALSE}
p_overlay <- plot_ss_result2(CBSBPB_data[result_index1,]$ss_res[[1]],
                             CBSBPB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay
```

@@

```{r CB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in CB functional group."), echo=FALSE}
CB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_CB_var.RDS"))
p3  <- plot_ss_result1(CB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p3
```

```{r CB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and CB functional groups."), echo=FALSE}
p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
                             CB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay
```

```{r SB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in SB functional group."), echo=FALSE}
SB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_SB_var.RDS"))
p4  <- plot_ss_result1(SB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p4

@@

```{r SB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and SB functional group."), echo=FALSE}
p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
                             SB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))

@@

## Figure: PB Stable states with variation and tradeoff

```{r PB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in PB functional group."), echo=FALSE}
PB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_PB_var.RDS"))
p5  <- plot_ss_result1(PB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p5

@@

```{r PB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and PB functional group."), echo=FALSE}
p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
                             PB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))

@@

## Figure: SBPB Stable states with variation and tradeoff

```{r SBPB_var1, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in SB and PB functional groups."), echo=FALSE}
SBPB_data <- readRDS(here("simulations/expt1/data/ss_res_grad_SBPB_var.RDS"))
p6  <- plot_ss_result1(SBPB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p6

```{r SBPB_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Diversity in none (solid) and SB and PB functional groups."), echo=FALSE}
p_overlay <- plot_ss_result2(CB_data[result_index1,]$ss_res[[1]],
                             SBPB_data[result_index2,]$ss_res[[1]],
                             xlims = c(-7, -1))

@@

```{r echo=FALSE, eval = FALSE}
#ss_sim_data <- readRDS(here("simulations/expt1/data/ss_res_3.RDS"))

CBSBPB_stab_data <- CBSBPB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results1 <- unnest(CBSBPB_stab_data, cols = c(stability_measures)) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

CB_stab_data <- CB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results2 <- unnest(CB_stab_data, cols = c(stability_measures))  %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SB_stab_data <- SB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))

# for(i in 1:20) {
#   print(i)
#   junk <- get_stability_measures(SB_data$ss_res[[i]])
# }
# ss_object <- SB_data$ss_res[[11]]
# 
# temp2 <- filter(temp, Species == "PB_1")
# get_hysteresis_total(log10(temp2$up+1), log10(temp2$down+1))
# down <- log10(temp2$down+1)
# up <- log10(temp2$up+1)
#

results3 <- unnest(SB_stab_data, cols = c(stability_measures))  %>%
  mutate(var_treat = "SB",
         var_gmax = SB_var_gmax_s)

PB_stab_data <- PB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results4 <- unnest(PB_stab_data, cols = c(stability_measures))  %>%
  mutate(var_treat = "PB",
         var_gmax = PB_var_gmax_s)

SBPB_stab_data <- SBPB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results5 <- unnest(SBPB_stab_data, cols = c(stability_measures))  %>%
  mutate(var_treat = "SB-PB",
         var_gmax = SB_var_gmax_s)

all_stab_results <- results1 %>%
  bind_rows(results2) %>%
  bind_rows(results3) %>%
  bind_rows(results4) %>%
  bind_rows(results5)

all_stab_results<- all_stab_results %>%
  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB", "PB", "SB-PB", "CB-SB-PB")))

saveRDS(all_stab_results, here("simulations/sim data/stab_measures.RDS"))

```{r ss_var3, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}

all_stab_results <- readRDS(here("simulations/expt1/data/stab_measures.RDS"))

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Community\ncomposition")
```

```{r ss_var4, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Community\ncomposition")

### 2021-06-24 manuscript/article.tex
made two experiments

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\begin{itemize}
\item
  In general, greater functional response diversity may decrease the
  likelihood of a catastrophic ecosystem response (Figure 2a in Dakos et
  al. (2019)). Here, we interpret this prediction to be that greater
  functional response diversity decreases the non-linearity of ecosystem
  response to environmental driver change, including the extreme
  non-linearity that can occur when an ecosystem ``flips'' from one
  state to another one.
\item
  Greater functional trait diversity can make a tipping point occur only
  with greater change in an environmental driver (Figure 2a in Dakos et
  al. (2019)). I.e. functional trait diversity can increase
  resilience--the extent of environmental change required to push the
  ecosystem into another state (Holling (1973)). This could occur if
  greater functional diversity equates to the presence of organisms with
  greater tolerance to the environmental driver Dakos et al. (2019).
\item
  On the other hand, the opposite could occur: greater functional
  diversity could make a tipping point occur with less change in an
  environmental driver (i.e.~may cause lower resilience) (Figure 2c in
  @dakos2019b). This could occur if there is selection for greater
  tolerance that causes, incidentally, selection for lower growth rate,
  perhaps due to a tradeoff between the two traits.
\item
  Finally, the amount of functional diversity may affect the ``recovery
  trajectory,'' i.e.~the relationship between ecosystem state and the
  environmental driver when the driver change is reversed Dakos et al.
  (2019). Put another way, functional diversity may increase or decrease
  the amount of hysteresis, and may even result in a recovery with lower
  non-linearity / no tipping-point (Figure 3 in Dakos et al. (2019)).
\end{itemize}

@@

\begin{itemize}
\item
  Mathematical modelling of a microbrial ecosystem. Trait diversity
  manipulation (can be considered selection among strains, or selection
  among species). (Do not include mutation or recomination).
\item
  Variation in amount of among strain variation, no variation in number
  of strains, no variation in strength or shape of the of the tradeoff.
\item
  Measurement of the effect on how the steady state(s) of the system
  varies with in different environmental conditions, and on the
  dynamical response of system to gradual environmental change.
\end{itemize}

@@

Each of the strains within each functional groups has its own parameter
set and state variable. Thus a system with nine strains within each
functional group has 27 state variables, plus another four (one for each
of the four chemical substrates). Other than having potentially
different parameter values (e.g.~maximum growth rate and tolerance
parameter) the dynamics of the strains in a functional were described by
the same equations. Hence, when parameterised with multiple strains per
functional group, but no variation among strains (within functional
groups), the system behaves identically to when there is only one strain
per functional group (see the \texttt{microxanox} R package \emph{User
Guide} for a demonstration).

@@

\caption{your caption}\label{fig:ss_novar}
\end{figure}

@@

\hypertarget{figure-stable-states-with-variation-and-tradeoff}{%
\subsection{Figure: Stable states with variation and
tradeoff}\label{figure-stable-states-with-variation-and-tradeoff}}

@@

\caption{your caption}\label{fig:ss_var}
\end{figure}

@@

\caption{your caption}\label{fig:ss_var2}
\end{figure}

@@

@@

@@

To be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).

@@

>>>>

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\begin{itemize}
\item
  In general, greater functional response diversity may decrease the
  likelihood of a catastrophic ecosystem response (Figure 2a in Dakos et
  al. (2019)). Here, we interpret this prediction to be that greater
  functional response diversity decreases the non-linearity of ecosystem
  response to environmental driver change, including the extreme
  non-linearity that can occur when an ecosystem ``flips'' from one
  state to another one.
\item
  Greater functional trait diversity can make a tipping point occur only
  with greater change in an environmental driver (Figure 2a in Dakos et
  al. (2019)). I.e. functional trait diversity can increase
  resilience--the extent of environmental change required to push the
  ecosystem into another state (Holling (1973)). This could occur if
  greater functional diversity equates to the presence of organisms with
  greater tolerance to the environmental driver Dakos et al. (2019).
\item
  On the other hand, the opposite could occur: greater functional
  diversity could make a tipping point occur with less change in an
  environmental driver (i.e.~may cause lower resilience) (Figure 2c in
  Dakos et al. (2019)). This could occur if there is selection for
  greater tolerance that causes, incidentally, selection for lower
  growth rate, perhaps due to a tradeoff between the two traits.
\item
  Finally, the amount of functional diversity may affect the ``recovery
  trajectory,'' i.e.~the relationship between ecosystem state and the
  environmental driver when the driver change is reversed Dakos et al.
  (2019). Put another way, functional diversity may increase or decrease
  the amount of hysteresis, and may even result in a recovery with lower
  non-linearity / no tipping-point (Figure 3 in Dakos et al. (2019)).
\end{itemize}

@@

\begin{itemize}
\item
  Mathematical modelling of a microbrial ecosystem. Trait diversity
  manipulation (can be considered selection among strains, or selection
  among species). (Do not include mutation or recomination).
\item
  Variation in amount of among strain variation, no variation in number
  of strains, no variation in strength or shape of the of any tradeoff.
\item
  Measurement of the effect on how the steady state(s) of the system
  varies with in different environmental conditions, and on the
  dynamical response of system to gradual environmental change.
\end{itemize}

@@

Each of the strains within each functional groups has its own parameter
set and state variable. Thus a system with nine strains within each
functional group has 27 state variables, plus another four (one for each
of the four chemical substrates). Other than having potentially
different parameter values (e.g.~maximum growth rate and tolerance
parameters) the dynamics of the strains in a functional were described
by the same equations. Hence, when parameterised with multiple strains
per functional group, but no variation among strains (within functional
groups), the system behaves identically to when there is only one strain
per functional group (see the \texttt{microxanox} R package \emph{User
Guide} for a demonstration).

@@

\caption{No diversity}\label{fig:ss_novar}
\end{figure}

@@

\hypertarget{figure-cbsbpb-stable-states-with-variation-and-tradeoff}{%
\subsection{Figure: CBSBPB Stable states with variation and
tradeoff}\label{figure-cbsbpb-stable-states-with-variation-and-tradeoff}}

@@

\caption{Diversity in all functional groups}\label{fig:ss_var}
\end{figure}

@@

\caption{Diversity in none (solid) and all functional groups.}\label{fig:ss_var2}
\end{figure}

@@

\hypertarget{figure-cb-stable-states-with-variation-and-tradeoff}{%
\subsection{Figure: CB Stable states with variation and
tradeoff}\label{figure-cb-stable-states-with-variation-and-tradeoff}}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/CB_var1-1}

\caption{Diversity in CB functional group.}\label{fig:CB_var1}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/CB_var2-1}

\caption{Diversity in none (solid) and CB functional groups.}\label{fig:CB_var2}
\end{figure}

\hypertarget{figure-sb-stable-states-with-variation-and-tradeoff}{%
\subsection{Figure: SB Stable states with variation and
tradeoff}\label{figure-sb-stable-states-with-variation-and-tradeoff}}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SB_var1-1}

\caption{Diversity in SB functional group.}\label{fig:SB_var1}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SB_var2-1}

\caption{Diversity in none (solid) and SB functional group.}\label{fig:SB_var2}
\end{figure}

\hypertarget{figure-pb-stable-states-with-variation-and-tradeoff}{%
\subsection{Figure: PB Stable states with variation and
tradeoff}\label{figure-pb-stable-states-with-variation-and-tradeoff}}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/PB_var1-1}

\caption{Diversity in PB functional group.}\label{fig:PB_var1}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/PB_var2-1}

\caption{Diversity in none (solid) and PB functional group.}\label{fig:PB_var2}
\end{figure}

\hypertarget{figure-sbpb-stable-states-with-variation-and-tradeoff}{%
\subsection{Figure: SBPB Stable states with variation and
tradeoff}\label{figure-sbpb-stable-states-with-variation-and-tradeoff}}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SBPB_var1-1}

\caption{Diversity in SB and PB functional groups.}\label{fig:SBPB_var1}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/SBPB_var2-1}

\caption{Diversity in none (solid) and SB and PB functional groups.}\label{fig:SBPB_var2}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{article_files/figure-latex/ss_var4-1}

\caption{your caption}\label{fig:ss_var4}
\end{figure}

@@

Maybe\ldots{} to be added. Need to go both ways (oxic to anoxic, and
anoxic to oxic).

@@

\hypertarget{further-relaxing-the-assumptions}{%
\subsection{Further relaxing the
assumptions}\label{further-relaxing-the-assumptions}}

Deterministic -\textgreater{} stochastic :
www.pnas.org/cgi/doi/10.1073/pnas.1414708112
